Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-03-20 paper/main.tex
Table 1: add numbers

\begin{table}[t]
  \caption{LTL to automata translators used for the experimental
    evaluation and the numbers of fails and successfully constructed
    automata with less than two marks and with at least two marks.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
\begin{tabular}{lrrrr}
  \toprule
  &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
  tool &\!\!\!version/homepage & fails & 0 or 1 mark & \textbf{at least 2 marks}\\
  \midrule
  \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
       & ? & ? & \textbf{129} \\
  \texttt{ltl2dgra} & 21.0\footnotemark[1]
       & ? & ? & \textbf{234}\\
  \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
       & ? & ? & \textbf{70}\\
  \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
       & ? & ? & \textbf{91}\\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \caption{LTL to automata translators used for the experimental
    evaluation and the numbers of fails and successfully constructed
    automata with less than two marks and with at least two marks.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
\begin{tabular}{lrrrr}
  \toprule
  &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
  tool &\!\!\!version/homepage & fails & 0 or 1 mark & \textbf{at least 2 marks}\\
  \midrule
  \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
       & 5 & 214 & \textbf{129} \\
  \texttt{ltl2dgra} & 21.0\footnotemark[1]
       & 12 & 102 & \textbf{234}\\
  \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
       & 0 & 278 & \textbf{70}\\
  \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
       & 18 & 239 & \textbf{91}\\
  \bottomrule
\end{tabular}
\end{table}
